Enzo+Moray: Radiation Hydrodynamics Adaptive Mesh Refinement Simulations with Adaptive Ray Tracing

### 2010-08-20 ms.tex
Added description of optically-thin approximation artifacts.

In practice, we have found it difficult to transition from this
optically-thin approximation to the optically-thick regime without
producing artifacts in the photo-ionization rate \kph.  The artifacts
exist in cells that intersect the $\tau_{\rm thin} \equiv 0.1$
surface.  These cells are split into the optically thin and thick
definitions, and we have not determined a good technique to avoid any
artifacts.  We use the optically thin problem used in the angular
resolution test (\S\ref{sec:ang_dep}) to show these artifacts in \kph.

>>>>

In practice, we have found it difficult to transition from this
optically-thin approximation to the optically-thick regime without
producing artifacts in the photo-ionization rate \kph.  We use the
optically thin problem used in the angular resolution test
(\S\ref{sec:ang_dep}) with $\Phi_c = 5.1$ to show these artifacts in
\kph~in Figure \ref{fig:rayopt}.  The radiation field strictly follows
a $1/r^2$ profile until it reaches $\tau_{\rm thin} \equiv 0.1$, which
is denoted by the white quarter circle in the figure.  At this radius,
the rays are then split until a sampling of $\Phi_c$ is satisfied.
Angular spike artifacts beyond this radius arise because of the
interface between the optically-thin approximation and full ray
tracing treatment.  They originate in cells that intersect the
$\tau_{\rm thin}$ surface, which are split into the optically thin and
thick definitions.  Unfortunately we have not determined a good
technique to avoid such artifacts.  They occur because of the
following reason.  When the first ray with $\tau < 0.1$ exits such a
cell, it applies the optically-thin approximation and marks the cell
so no other ray from the same source contributes to its \kph~and
$\Gamma$ field.  However other rays may exit the cell with $\tau >
0.1$ because the maximum distance between the far cell faces and the
source is not always $\tau < 0.1$.  Then these rays will split in this
cell and add to \kph~and become attenuated, reducing its photon
fluxes.  When the rays continue to the next cell after this
transition, the photon fluxes are not necessarily equal to each other,
creating the angular artifacts seen in Figure \ref{fig:rayopt}.  We
are continuing to formulate a scheme that avoids these artifacts
because this approximation will be very advantageous in simulations
with large ionized filling factors.
